---
title: "Analysis"
author: "ABB"
date: "2023-05-30"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)

# green is the reconciled one
# (NOT to be answered by REVIEWER) Has the study been reconciled?_cb623db2-5f5e-4676-9497-f22d4d58fd02 == YES is reconciled

```

## Diagram of analysis to be carried out

https://lucid.app/lucidchart/07544fa2-2781-40f0-b03b-d3d3595d9443/edit?viewport_loc=-325%2C-1822%2C3711%2C2979%2C0_0&invitationId=inv_b89952a6-b78e-49f7-9d45-e64aa7af5638 

for simple diagrams, a 

for complex connections - sankey diagram - for the link between printing methods + printing model --> link to the bioink type (+ origin)?

first things first, to give numbers of studies that report e.g. A or B

## Printing Techniques 

Give an overview of the different printing techniques, 
- method
- printer model
- printer source
- forms 
- software 



```{r printing-techniques, echo = TRUE}



```

## BioInks

Give an overview of the different inks used with these techniques. 
- type
- origin
- additives
- density

```{r printing-inks, echo=TRUE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.



## Liver Cells
And then it is liver specific variables. 
- main type of liver cells 
- info about liver cells

AN - Main type of liver cells

if comments from reconciled - print out for all to see. 

if any of reviewer comments say HepG2 

```{r liver-cells}



```


## Cells 
What types of included cells? 
- human, animal, both
```{r}

```


## Culture Conditions
What tpye of culture conditions? 
Liver Markers- what measurements? 
```{r}

```


## Quality
Quality Assays, storage conditions 
```{r}

```


